The ppmData R-package for setting up spatial point process models

### 2022-08-10 paper/paper.Rmd
update to text and figure

# Inhomogeneous Poisson Process Models (IPPM)

An IPPM is a statistical model used to describe a random point pattern for $n$ observed locations, ($\bm{y}=(y(\bm{s}_1),y(\bm{s_2}),\ldots,y(\bm{s}_n))$, in a spatial window $\mathcal{A}\subset R^2$. An IPPM is based on the assumption that the number of points, $n$, is a Poisson random variable, with spatially varying intensity $\Lambda = \int_{\bm{s}\in\mathcal{A}}\lambda(\bm{s})d\bm{s}$, and that the spatial locations of $\bm{y}$ are independently drawn from the spatial surface [e.g. @cressie_statistics_1993]. For convenience, we define (for example) $\lambda(\bm{s}_i)$ as the intensity surface of the point process at the $i^{th}$ location $\bm{s}_i$. The intensity surface can be defined as $\log\{\lambda_i\}=\bm{x}_i^{\top}\bm{\beta}$ where $\bm{x}_i$ is a vector of spatially located covariates and $\bm{\beta}$ is a corresponding vector of coefficients.

>>>>

# Inhomogeneous Poisson Process Models

An Inhomogeneous Poisson Process Models is a statistical model used to describe a random point pattern for $n$ observed locations, ($\bm{y}=(y(\bm{s}_1),y(\bm{s_2}),\ldots,y(\bm{s}_n))$, in a spatial window $\mathcal{A}\subset R^2$. An Inhomogeneous Poisson Process Model assumes that the number of points, $n$, is a Poisson random variable, with spatially varying intensity $\Lambda = \int_{\bm{s}\in\mathcal{A}}\lambda(\bm{s})d\bm{s}$, and that the spatial locations of $\bm{y}$ are independently drawn from the spatial surface [e.g. @cressie_statistics_1993]. For convenience, we define (for example) $\lambda(\bm{s}_i)$ as the intensity surface of the point process at the $i^{th}$ location $\bm{s}_i$. The intensity surface can be defined as $\log\{\lambda_i\}=\bm{x}_i^{\top}\bm{\beta}$ where $\bm{x}_i$ is a vector of spatially located covariates and $\bm{\beta}$ is a corresponding vector of coefficients.
